---
title: "Rectangling Lab"
author: "Sha Lu"
date: "6/14/2021"
output: pdf_document
---

```{r}
library(rvest)
library(dplyr)
library(tidyverse)
library(repurrrsive)
listviewer::jsonedit(gh_users)
```
a) Explain or describe nested Lists. 
```{r}
## Nested list means there are lists inside a list. 
```
b) Open and explore data for Git Hub repos by running the following code gh_repos.  Comment on the structure and arrangement of the data (Two or three sentences)
```{r}
listviewer::jsonedit(gh_repos)
## This is an array with 6 nested lists inside. Every list except list 3 has 30 sub-lists, list 3 has 26 sub-lists. Under the sub-lists, there are 68 elements or objects sepreatly. 
```
c)  In two or three sentences, explain what happens to the data when you run the code
```{r}
repos <- tibble(repo = gh_repos)
repos

## This code organizes the data into a tibble. Whole repo has 6 lists. Every list has 30 sub lists.
```
d)  Describe the data representation when the listserver tool is applied. And go into detail explaining why we have a nested List configuration. What do the numbers 30 and 68 represent ? (6 or 7 sentences)
```{r}
listviewer::jsonedit(gh_repos)
## This array has 6 lists. Under every list, there are 30 sub-lists. Except list 3 has only 26 sub-list. Every sub-list is a user's information, it has 68 elements.
```
e)
```{r}
tibble(repo = gh_repos)%>%
  unnest_auto(repo)%>%
  unnest_auto(repo) -> new
new

```

